---
title: "Validation of Lung Markers for Erlotinib."
output:
  html_document:
    df_print: paged
  html_notebook: default
---

# Lung + Erlotinib

This should be fairly simple, there is 1 dataset.



```{r}


library(PharmacoGx)
library(survcomp)
library(survminer)
library(readxl)
library(ggplot2)
library(qs)

library(data.table)


biomarker_res <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res//mrna_gene_drug_tissue_res_pharmacodb.csv")

biomarker_res <- biomarker_res[FWER_genes <= 0.05]



geneToCorrelate <- biomarker_res[Tissue=="Lung"&Drug=="Erlotinib", Gene]



battle1.se <- qread("~/Code/univariate_rna_validation/data/Clinical Trial SE/GSE33072_SE.qs")

battle1.erlotinib <- battle1.se[,battle1.se$treatment %in% "erlotinib"] #note, missing 1 patient on "erlotinib+bexarotene"


summary(as.numeric(battle1.erlotinib$survival_time))
battle1.erlotinib$event_occured <- ifelse(battle1.erlotinib$progression.free.survival.status.ch1 %in% 1, 1, 0)


```



In this case, we have multiple markers to look at, and not too many patients. Therefore, we will apply the filters from Task 1 to narrow down the search space to only those that aren't rejected as "too different" between cell lines and patients. 

Lets check all the markers in a loop:


Now we can check the correlation with survival using the concordance index. Unfortunately, there are no labels for "response" in the erlotinib cohort. 

The way the following code is designed, we use the sign of the estimate from the cell line analysis to make higher c-index correspond to predictions in the same direction as cell lines. 

Note that the p values from surv.comp are known to be anti-conservative, so we confirm with a permutation test. 


```{r}
library(parallel)
cl=makeCluster(24)

clusterExport(cl=cl, c("biomarker_res", "battle1.erlotinib"))

permutation.res <- parallel::parSapply(cl=cl, geneToCorrelate, \(gene) {
  # gene <- "ENSG00000116670"
  gene.exp <- SummarizedExperiment::assay(battle1.erlotinib)[gene, ]

## Using Hmisc because it is much faster
  obs <- Hmisc::rcorr.cens(sign(biomarker_res[Tissue == "Lung" & Drug == "Erlotinib" & Gene == gene, estimate]) * gene.exp, 
                           survival::Surv(as.numeric(battle1.erlotinib$survival_time), battle1.erlotinib$event_occured))[[1]]

  perms <- sapply(1:100000, function(i) {
  Hmisc::rcorr.cens(sign(biomarker_res[Tissue == "Lung" & Drug == "Erlotinib" & Gene == gene, estimate]) * sample(gene.exp),
                    survival::Surv(as.numeric(battle1.erlotinib$survival_time), battle1.erlotinib$event_occured))[[1]]
})

  p.val <- mean(abs(obs - 0.5) < abs(perms - 0.5))
  return(c("CI" = obs, p.value = p.val))
})

stopCluster(cl)

permutation.res

```


```{r}




# load("~/Data/Task1 Filter/results_01112022/AD/ad.cancer.type.ccle.RData")
load("~/Code/tissue_biomarker/farnoosh_ks_res/results/ad.res.scale.RData")
ad.res <- data.table(ad.res)

ad.res[,mean(padj.BH<.1), cancer]


# merged.biomarker.res <- merge(biomarker_res, ad.res, by.x=c("Gene", "Tissue"), by.y=c("gene", "lineage"))
# # merged.biomarker.res[Gene %in% names(concordance.index.res[sapply(concordance.index.res, function(x) return(x$p.value < 0.001))])&Drug=="Erlotinib"]
# geneToCorrelate <- merged.biomarker.res[Gene %in% geneToCorrelate&Drug=="Erlotinib"&padj.BH>0.1, Gene]

geneToCorrelate <- intersect(ad.res[cancer == "lung" & padj.BH > 0.1, gene], geneToCorrelate)


```


We can check if applying this filter would allow us to detect a significant effect. 


```{r}
library(parallel)
cl=makeCluster(24)

clusterExport(cl=cl, c("biomarker_res", "battle1.erlotinib"))

permutation.res <- parallel::parSapply(cl=cl, geneToCorrelate, \(gene) {
  # gene <- "ENSG00000116670"
  gene.exp <- SummarizedExperiment::assay(battle1.erlotinib)[gene, ]

## Using Hmisc because it is much faster
  obs <- Hmisc::rcorr.cens(sign(biomarker_res[Tissue == "Lung" & Drug == "Erlotinib" & Gene == gene, estimate]) * gene.exp, 
                           survival::Surv(as.numeric(battle1.erlotinib$survival_time), battle1.erlotinib$event_occured))[[1]]

  perms <- sapply(1:100000, function(i) {
  Hmisc::rcorr.cens(sign(biomarker_res[Tissue == "Lung" & Drug == "Erlotinib" & Gene == gene, estimate]) * sample(gene.exp),
                    survival::Surv(as.numeric(battle1.erlotinib$survival_time), battle1.erlotinib$event_occured))[[1]]
})

  p.val <- mean(abs(obs - 0.5) < abs(perms - 0.5))
  return(c("CI" = obs, p.value = p.val))
})

stopCluster(cl)

permutation.res
```


For plotting purposes, we will look at a Kaplan Meier, however it is not a significant marker when you binarize using the median. 

```{r}

library(survcomp)
library(survminer)
library(ggplot2)


png("figures/mad2l2_pfs_km.png", res=600, height = 5, width=5, units="in")
surv.data <- data.frame(time=as.numeric(battle1.erlotinib$survival_time), event=battle1.erlotinib$event_occured, MAD2L2=ifelse(assay(battle1.erlotinib)["ENSG00000116670",]>median(assay(battle1.erlotinib)["ENSG00000116670",]),"High", "Low"))
ggsurvplot(survfit(Surv(time, event=event)~MAD2L2, surv.data), pval=F)
dev.off()


```


# Checking prognosis and healthy vs disease tissue

```{r}
library(UCSCXenaTools)
XenaGenerate(subset = XenaHostNames=="tcgaHub") %>% 
  XenaFilter(filterDatasets = "clinical|HiSeqV2$") %>% 
  XenaFilter(filterDatasets = "LUAD") -> df_todo

XenaQuery(df_todo) %>% XenaDownload() %>% XenaPrepare() -> LUAD



```

```{r}

MAD2L2.tcga <- unlist(LUAD$HiSeqV2.gz[LUAD$HiSeqV2.gz$sample=="MAD2L2",-1])

hist(MAD2L2.tcga)


```


```{r}

LUAD.pfs.event <- !is.na(LUAD$LUAD_clinicalMatrix$days_to_new_tumor_event_after_initial_treatment)

LUAD.pfs.time <- ifelse(LUAD.pfs.event, LUAD$LUAD_clinicalMatrix$days_to_new_tumor_event_after_initial_treatment, LUAD$LUAD_clinicalMatrix$days_to_last_followup)

common.patients <- intersect(LUAD$LUAD_clinicalMatrix$sampleID, names(MAD2L2.tcga))

surv.order <- match(common.patients, LUAD$LUAD_clinicalMatrix$sampleID)

exp.order <- match(common.patients, names(MAD2L2.tcga))

## Using Hmisc because it is much faster
obs <- Hmisc::rcorr.cens(MAD2L2.tcga[exp.order],Surv(as.numeric(LUAD.pfs.time)[surv.order], LUAD.pfs.event[surv.order]))[[1]]

perms <- sapply(1:1000, function(i) 
Hmisc::rcorr.cens(MAD2L2.tcga[sample(exp.order)],Surv(as.numeric(LUAD.pfs.time)[surv.order], LUAD.pfs.event[surv.order]))[[1]]
)

mean(abs(obs-0.5)<abs(perms-0.5))


```

There seems to be no association among the TCGA patients with PFS, although the definitions of PFS are very different between these datasets. 



```{r}

library(survcomp)
library(survminer)
library(ggplot2)


png("figures/mad2l2_pfs_km_TCGA.png", res = 600, height = 5, width = 5, units = "in")
surv.data <- data.frame(Days=as.numeric(LUAD.pfs.time)[surv.order], event=LUAD.pfs.event[surv.order], 
                        MAD2L2=ifelse(MAD2L2.tcga[exp.order]>median(MAD2L2.tcga[exp.order]),"High", "Low"))
ggsurvplot(survfit(Surv(Days, event=event)~MAD2L2, surv.data), pval=F)
dev.off()


```


