---
title: "Lymphoid Validation of Doxorubicin markers."
output:
  html_document:
    df_print: paged
---

# Lymphoid + Doxorubicin

Just one public dataset here, but I can check several biomarkers. 

```{r}

suppressPackageStartupMessages({
library(PharmacoGx)
library(readxl)
library(ggplot2)
library(qs)
library(stringr)

library(data.table)
})


biomarker_res <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")

biomarker_res <- biomarker_res[FWER_genes <= 0.05]

biomarker_res[Tissue == "Lymphoid" & Drug == "Doxorubicin"]

genesToCorrelate <- biomarker_res[Tissue == "Lymphoid" & Drug == "Doxorubicin", Gene]


```


Lets load in both the datasets from the Winter study. 
```{r}
GSE14615_SE <- qread("~/Data/Clinical Trial SE/GSE14615_SE.qs")
GSE14613_SE <- qread("~/Data/Clinical Trial SE/GSE14613_SE.qs")

```

# First Looking at GSE14615_SE
```{r}
setdiff(genesToCorrelate, rownames(GSE14615_SE))
genesToCorrelate <- intersect(genesToCorrelate, rownames(GSE14615_SE))
```

```{r}

sapply(genesToCorrelate, function(gene){

    toTest <- data.frame(gene = assay(GSE14615_SE)[gene,], 
                      response = GSE14615_SE$response)
    
    kruskal.test(gene~response, toTest)
})


```


Lets plot both since there is only 2. Starting with the trending marker YIF1A (ENSG00000174851)


```{r}
gene.exp <- assay(GSE14615_SE)["ENSG00000174851", ]

toPlot <- data.frame(YIF1A = gene.exp, Response = GSE14615_SE$response, 
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("YIF1A Expression")

pdf("figures/GSE14615_YIF1A_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("YIF1A Expression")
dev.off()
```

Now with the marker GABRG2 (ENSG00000113327)


```{r}
gene.exp <- assay(GSE14615_SE)["ENSG00000113327", ]

toPlot <- data.frame(GABRG2 = gene.exp, Response = GSE14615_SE$response, 
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("GABRG2 Expression")

pdf("figures/GSE14615_GABRG2_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("GABRG2 Expression")
dev.off()
```



# Now Looking at GSE14613_SE
```{r}
setdiff(genesToCorrelate, rownames(GSE14613_SE))
genesToCorrelate <- intersect(genesToCorrelate, rownames(GSE14613_SE))
```

```{r}

sapply(genesToCorrelate, function(gene){

    toTest <- data.frame(gene = assay(GSE14613_SE)[gene,], 
                      response = GSE14613_SE$response)
    
    kruskal.test(gene~response, toTest)
})


```


Lets plot both since there is only 2. Starting with the trending marker YIF1A (ENSG00000174851). 


```{r}
gene.exp <- assay(GSE14613_SE)["ENSG00000174851", ]

toPlot <- data.frame(YIF1A = gene.exp, Response = GSE14613_SE$response, 
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("YIF1A Expression")

pdf("figures/GSE14613_YIF1A_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("YIF1A Expression")
dev.off()
```

Now with the marker GABRG2 (ENSG00000113327)


```{r}
gene.exp <- assay(GSE14613_SE)["ENSG00000113327", ]

toPlot <- data.frame(GABRG2 = gene.exp, Response = GSE14613_SE$response, 
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("GABRG2 Expression")

pdf("figures/GSE14613_GABRG2_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("GABRG2 Expression")
dev.off()
```

# Combining the two datasets naively


```{r}

sapply(genesToCorrelate, function(gene){

    toTest <- data.frame(gene = c(assay(GSE14613_SE)[gene,],assay(GSE14615_SE)[gene,]), 
                      response = c(GSE14613_SE$response, GSE14615_SE$response) )
    
    kruskal.test(gene~response, toTest)
})


```



```{r}
gene.exp <- c(assay(GSE14613_SE)["ENSG00000174851", ], 
              assay(GSE14615_SE)["ENSG00000174851", ])

toPlot <- data.frame(YIF1A = gene.exp, Response = c(GSE14613_SE$response, GSE14615_SE$response), 
                     dataset = c(rep("GSE14613", times=ncol(GSE14613_SE)),rep("GSE14615", times=ncol(GSE14615_SE))),
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(x = YIF1A, fill = dataset)) +
     geom_density()

ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("YIF1A Expression")

pdf("figures/Winters_Combined_YIF1A_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("YIF1A Expression")
dev.off()
```

The batch effect seems too strong here to make this a meaningful comparison. 


```{r}
gene.exp <- c(
    assay(GSE14613_SE)["ENSG00000113327", ],
    assay(GSE14615_SE)["ENSG00000113327", ]
)


toPlot <- data.frame(
    GABRG2 = gene.exp, Response = c(GSE14613_SE$response, GSE14615_SE$response),
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(x = GABRG2, fill = dataset)) +
    geom_density()

ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("GABRG2 Expression")

pdf("figures/GSE14613_GABRG2_Boxplot.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("GABRG2 Expression")
dev.off()
```
The batch effect seems too strong here to make this a meaningful comparison. 

## Checking expression of "housekeeping gene" GAPDH (ENSG00000111640)


```{r}
gene.exp <- c(
    assay(GSE14613_SE)["ENSG00000111640", ],
    assay(GSE14615_SE)["ENSG00000111640", ]
)


toPlot <- data.frame(
    GAPDH = gene.exp, 
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)

ggplot(toPlot, aes(x = GAPDH, fill = dataset)) +
    geom_density()
```



## Checking expression of "housekeeping gene" ATXN2 (ENSG00000204842)


```{r}
gene.exp <- c(
    assay(GSE14613_SE)["ENSG00000204842", ],
    assay(GSE14615_SE)["ENSG00000204842", ]
)


toPlot <- data.frame(
    ATXN2 = gene.exp, 
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)

ggplot(toPlot, aes(x = ATXN2, fill = dataset)) +
    geom_density()
```


## Lets look at a PCA on common genes:



```{r}

library(GGally)

common.genes <- intersect(rownames(GSE14613_SE), rownames(GSE14615_SE))

gene.exp <- cbind(
    assay(GSE14613_SE)[common.genes, ],
    assay(GSE14615_SE)[common.genes, ]
)

pca <- prcomp(x=t(gene.exp))

ggpairs(as.data.frame(pca$x[, 1:5]), aes(color = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE)))))

```


# Batch effect corrected analysis together 
Looks like we have a signficant batch effect in this data. Lets try our analysis again with combat applied. 


```{r}
library(sva)


phData <- data.frame(
    Dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    Response = c(GSE14613_SE$response, GSE14615_SE$response),
    check.names = FALSE
)

combat.gene.exp <- ComBat(gene.exp, batch = phData$Dataset, mod=model.matrix(~Response, data=phData))


pca.combat <- prcomp(x = t(combat.gene.exp))

ggpairs(as.data.frame(pca.combat$x[, 1:5]), aes(color = phData$Dataset))


```

Unsurprisingly, ComBat obliterates the batch effects. 



## Checking expression of "housekeeping gene" GAPDH (ENSG00000111640)


```{r}
gene.exp <- c(
    combat.gene.exp["ENSG00000111640", ],
    combat.gene.exp["ENSG00000111640", ]
)


toPlot <- data.frame(
    GAPDH = gene.exp, 
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)

ggplot(toPlot, aes(x = GAPDH, fill = dataset)) +
    geom_density()
```


## Checking expression of "housekeeping gene" ATXN2 (ENSG00000204842)


```{r}
gene.exp <- c(
    combat.gene.exp["ENSG00000204842", ],
    combat.gene.exp["ENSG00000204842", ]
)


toPlot <- data.frame(
    ATXN2 = gene.exp, 
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)

ggplot(toPlot, aes(x = ATXN2, fill = dataset)) +
    geom_density()
```

## Combined biomarker analysis. 

```{r}

sapply(genesToCorrelate, function(gene){

    toTest <- data.frame(gene = combat.gene.exp[gene,], 
                      response = c(GSE14613_SE$response, GSE14615_SE$response))
    
    kruskal.test(gene~response, toTest)
})


```

```{r}
gene.exp <- c(combat.gene.exp["ENSG00000174851", ], 
              combat.gene.exp["ENSG00000174851", ])

toPlot <- data.frame(YIF1A = gene.exp, Response = c(GSE14613_SE$response, GSE14615_SE$response), 
                     dataset = c(rep("GSE14613", times=ncol(GSE14613_SE)),rep("GSE14615", times=ncol(GSE14615_SE))),
                     check.names = FALSE)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(x = YIF1A, fill = dataset)) +
     geom_density()

ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("YIF1A Expression")

pdf("figures/Winters_Combined_YIF1A_Boxplot_COMBAT.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, YIF1A)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("YIF1A Expression")
dev.off()
```

The batch effect seems too strong here to make this a meaningful comparison. 


```{r}
gene.exp <- c(
    combat.gene.exp["ENSG00000113327", ],
    combat.gene.exp["ENSG00000113327", ]
)


toPlot <- data.frame(
    GABRG2 = gene.exp, Response = c(GSE14613_SE$response, GSE14615_SE$response),
    dataset = c(rep("GSE14613", times = ncol(GSE14613_SE)), rep("GSE14615", times = ncol(GSE14615_SE))),
    check.names = FALSE
)
toPlot$Response <- str_to_title(trimws(gsub(".+\\=", "", toPlot$Response)))
toPlot$Response <- factor(toPlot$Response)
levels(toPlot$Response) <- c("Complete Continous\nRemission", "Failure\n(Relapse)", "No Response\n(Induction Failure)")

ggplot(toPlot, aes(x = GABRG2, fill = dataset)) +
    geom_density()

ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill = "lightgray") +
    theme_bw() + ylab("GABRG2 Expression")

pdf("figures/Winters_Combined_GABRG2_Boxplott_COMBAT.pdf", width = 4, height = 4)
ggplot(toPlot, aes(Response, GABRG2)) +
    geom_boxplot(fill="lightgray") +
    theme_bw() + ylab("GABRG2 Expression")
dev.off()
```

# Distribution of diseases in vitro

```{r}

GDSC1 <- updateObject(readRDS("~/Data/TBPInputs/archive_2022_04_08/rna/GDSC1.rds"))
GDSC2 <- updateObject(readRDS("~/Data/TBPInputs/archive_2022_04_08/rna/GDSC2.rds"))
CCLE.CTRPv2 <- updateObject(readRDS("~/Data/TBPInputs/archive_2022_04_08/rna/CCLE.CTRPv2.rds"))
gCSI <- updateObject(readRDS("~/Data/TBPInputs/archive_2022_04_08/rna/gCSI.rds"))
CCLE <- updateObject(readRDS("~/Data/TBPInputs/archive_2022_04_08/rna/CCLE.rds"))


pset.list <- list(GDSC1, GDSC2, tCCLE, CCLE.CTRPv2, gCSI)
names(pset.list) <- sapply(pset.list, name)

```


```{r}
disease.tables <- lapply(pset.list, \(pset){

    table(cellInfo(pset)$Cellosaurus.Disease[cellInfo(pset)$tissueid=="Lymphoid"])

})

all.disease <- .unionList(lapply(disease.tables, names))

disease.cell.count <- matrix(NA_integer_, nrow=length(all.disease), ncol=length(pset.list), dimnames=list(all.disease, names(pset.list)))

for(psetn in names(pset.list)){

    disease.cell.count[names(disease.tables[[psetn]]), psetn] <- as.numeric(disease.tables[[psetn]])

}

write.csv(disease.cell.count)
```


# SessionInfo

```{r}

sessionInfo()

```