---
title: "Breast Validation of Lapatinib markers."
output:
  html_document:
    df_print: paged
---

# Lapatinib + Breast

Just one public dataset here, but I can check several biomarkers. 

```{r}


library(PharmacoGx)
library(readxl)
library(ggplot2)
library(qs)
library(PRROC)


library(data.table)



biomarker_res <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")

biomarker_res <- biomarker_res[FWER_genes <= 0.05]

biomarker_res[Tissue == "Breast" & Drug == "Lapatinib"]

genesToCorrelate <- biomarker_res[Tissue == "Breast" & Drug == "Lapatinib", Gene]


```


Lets load in the dataset and start by examining the two arms separately.
```{r}
GSE66305_SE <- qread("~/Data/Clinical Trial SE/GSE66305_SE.qs")


```

Note that one of the biomarkers is not on the array:

```{r}
setdiff(genesToCorrelate, rownames(GSE66305_SE))
genesToCorrelate <- intersect(genesToCorrelate, rownames(GSE66305_SE))
```

## chemo+lapatinib arm.

```{r}
GSE66305_SE <- qread("~/Data/Clinical Trial SE/GSE66305_SE.qs")

GSE66305_SE_lapatinib_only <- GSE66305_SE[,"chemotherapy+lapatinib"==GSE66305_SE$treatment]

```

```{r}

data.frame(sapply(genesToCorrelate, function(gene){

    gene.exp <- assay(GSE66305_SE_lapatinib_only)[gene, ]

    wilcox.test(
        split(gene.exp, f = GSE66305_SE_lapatinib_only$response)[[1]],
        split(gene.exp, f = GSE66305_SE_lapatinib_only$response)[[2]]
    )$p.value
}))


```


## chemo+lapatinib+herceptin arm.

```{r}
GSE66305_SE <- qread("~/Data/Clinical Trial SE/GSE66305_SE.qs")

GSE66305_SE_combo <- GSE66305_SE[, "chemotherapy+trastuzumab+lapatinib" == GSE66305_SE$treatment]

```

```{r}

data.frame(sapply(genesToCorrelate, function(gene){

    gene.exp <- assay(GSE66305_SE_combo)[gene, ]

    wilcox.test(
        split(gene.exp, f = GSE66305_SE_combo$response)[[1]],
        split(gene.exp, f = GSE66305_SE_combo$response)[[2]]
    )$p.value
}))


```


# AD filter

Now Lets check what this looks like if we pre-filter using the AD filter


```{r}

# load("~/Data/Task1 Filter/results_01112022/AD/ad.cancer.type.ccle.RData")
load("~/Code/tissue_biomarker/farnoosh_ks_res/results/ad.res.scale.RData")
ad.res <- data.table(ad.res)


genesToCorrelate <- intersect(ad.res[cancer == "breast" & padj.BH > 0.1, gene], genesToCorrelate)


```

Looking at the chemo+lapatinib arm.

```{r}
GSE66305_SE <- qread("~/Data/Clinical Trial SE/GSE66305_SE.qs")

GSE66305_SE_lapatinib_only <- GSE66305_SE[,"chemotherapy+lapatinib"==GSE66305_SE$treatment]

```


```{r}

sapply(genesToCorrelate, function(gene){
    gene.exp <- assay(GSE66305_SE_lapatinib_only)[gene, ]

    wilcox.test(
        split(gene.exp, f = GSE66305_SE_lapatinib_only$response)[[1]],
        split(gene.exp, f = GSE66305_SE_lapatinib_only$response)[[2]]
    )$p.value
})


```

With the filter, ENSG00000141738 (GRB7) protein expression is significant. 


```{r}
GSE66305_SE_lapatinib <- GSE66305_SE[, grepl("lapatinib",x=GSE66305_SE$treatment)]



gene.exp <- assay(GSE66305_SE_lapatinib)["ENSG00000141738", ]

toPlot <- data.frame(GRB7 = gene.exp, Response = GSE66305_SE_lapatinib$response, 
                     `Treatment Arm` = GSE66305_SE_lapatinib$treatment, 
                     check.names = FALSE)

toPlot[, "Treatment Arm"] <- ifelse(toPlot[, "Treatment Arm"] == "chemotherapy+lapatinib", 
                                    "Chemo + Lapatinib",
                                    "Chemo + Lapatinib + Trastuzumab")

ggplot(toPlot, aes(Response, GRB7)) +
    geom_boxplot(fill = "lightgray") +
    facet_grid(. ~ `Treatment Arm`) +
    theme_bw() + ylab("GRB7 Expression")

pdf("figures/GSE66305_GRB7_StartByTreatment.pdf", width = 7, height = 5)
ggplot(toPlot, aes(Response, GRB7)) +
    geom_boxplot(fill="lightgray") +
    facet_grid(. ~ `Treatment Arm`) +
    theme_bw() + ylab("GRB7 Expression")
dev.off()

```

Lets plot the ROC and PR curves within the Chemo+Lap arm

```{r}

gene.exp <- assay(GSE66305_SE_lapatinib_only)["ENSG00000141738", ]
status <- GSE66305_SE_lapatinib_only$response

plot(roc.curve(gene.exp, weights.class0 = status == "pCR", curve = T),
    color = FALSE, auc.main = FALSE,
    main = paste0("ROC Curve\nAUC = ", format(roc.curve(gene.exp, weights.class0 = status == "pCR", curve = T)$auc, digits = 2))
)
lines(seq(0, 1, 0.01), seq(0, 1, 0.01))



pdf("figures/GSE66305_GRB7_ROC.pdf", width = 5, height = 5)
plot(roc.curve(gene.exp, weights.class0 = status == "pCR", curve = T),
    color = FALSE, auc.main = FALSE,
    main = paste0("ROC Curve\nAUC = ", format(roc.curve(gene.exp, weights.class0 = status == "pCR", curve = T)$auc, digits = 2))
)
lines(seq(0, 1, 0.01), seq(0, 1, 0.01))
dev.off()

plot(pr.curve(gene.exp, weights.class0 = status == "pCR", curve = T),
    color = FALSE, auc.main = FALSE,
    main = paste0("PR Curve\nAUC = ", format(pr.curve(gene.exp, weights.class0 = status == "pCR", curve = T)$auc.integral, digits = 2))
)
lines(seq(0, 1, 0.01), rep(mean(status=="pCR"), times = length(seq(0, 1, 0.01))))


pdf("figures/GSE66305_GRB7_PR.pdf", width = 5, height = 5)
plot(pr.curve(gene.exp, weights.class0 = status == "pCR", curve = T),
    color = FALSE, auc.main = FALSE,
    main = paste0("PR Curve\nAUC = ", format(pr.curve(gene.exp, weights.class0 = status == "pCR", curve = T)$auc.integral, digits = 2))
)
lines(seq(0, 1, 0.01), rep(mean(status == "pCR"), times = length(seq(0, 1, 0.01))))
dev.off()

```
