---
title: "Ovarian Validation of Paclitaxel markers."
output:
  html_document:
    df_print: paged
---

# Ovarian + Taxol

There are a few datasets to look at here: 
GSE14764 - yes 
GSE15622 - yes 
GSE63885 - yes
GSE31245 - yes


Only 1 biomarker to check however.

```{r}


library(PharmacoGx)
library(survcomp)
library(survminer)
library(readxl)
library(ggplot2)
library(qs)

library(data.table)



biomarker_res <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")

biomarker_res <- biomarker_res[FWER_genes <= 0.05]

biomarker_res[Tissue=="Ovary/Fallopian Tube"]

geneToCorrelate <- biomarker_res[Tissue=="Ovary/Fallopian Tube"&Drug=="Paclitaxel", Gene]
as.res <- ad.res[cancer != "blood"]
fwrite(ad.res, "ad.res.compiled.csv")

```


## GSE63885_SE

This is a dataset with adjuvant taxane/plantinum (or other chemo, which we filter out).

```{r}
GSE63885_SE <- qread("~/Data/Clinical Trial SE/GSE63885_SE.qs")

GSE63885_taxane <- GSE63885_SE[, GSE63885_SE$treatment %in% "taxane/platinum"]

```


We can look at response, which is classified as a version of RECIST. 


First looking at response

```{r}

GJB1.exp <- assay(GSE63885_taxane)["ENSG00000169562", ]

# wilcox.test(split(GJB1.exp,GSE63885_taxane$residual.tumor.ch1)[[1]], split(GJB1.exp,GSE63885_taxane$residual.tumor.ch1)[[2]])

GSE63885_taxane$response[GSE63885_taxane$response=="P"] <- 'PD'

pdf("figures/GSE63885_gjb1_boxplot.pdf", width = 4, height = 4)
boxplot(split(GJB1.exp, GSE63885_taxane$response)[c("PD", "SD", "PR", "CR")], ylab = "log(RMA Expression)")
dev.off()
boxplot(split(GJB1.exp, GSE63885_taxane$response)[c("PD", "SD", "PR", "CR")], ylab = "log(RMA Expression)")

kruskal.test(GSE63885_taxane$response ~ GJB1.exp)

```



## GSE14764_SE

This is a dataset of adjuvant treated Paclitaxel + Carboplatin. 

PMID: 19294737


```{r}

ov.data <- qread("~/Data/Clinical Trial SE/GSE14764_SE.qs")

```

We can look at "response", in this trial quantified as residual tumour presence or absence, and survival. 

First looking at response:

```{r}

GJB1.exp <- assay(ov.data)["ENSG00000169562",]

wilcox.test(split(GJB1.exp, ov.data$residual.tumor.ch1)[[1]], split(GJB1.exp, ov.data$residual.tumor.ch1)[[2]])

toPlot <- split(GJB1.exp, ov.data$residual.tumor.ch1)
names(toPlot) <- c("No RD", "Residual Disease")

boxplot(toPlot, ylab = "log(RMA Expression)")

pdf("figures/GSE14764_gjb1_boxplot.pdf", width = 4, height = 4)
boxplot(toPlot, ylab = "log(RMA Expression)")
dev.off()

```

No association with "response". 

### Survival

Likewise, there is no 
```{r}

surv.data <-  colData(ov.data)[,c("overall.survival.event.ch1", "overall.survival.time.ch1")]

colnames(surv.data) <- c("event", 'time')
surv.data$time <- as.numeric(surv.data$time)
surv.data$event <- as.numeric(surv.data$event)


surv.data$GJB1 <- ifelse(GJB1.exp <= median(GJB1.exp), "low", "high")



ggsurvplot(survfit(Surv(time, event=event)~GJB1, surv.data), pval=T)



```


# GSE15622


```{r}
library(qs)

ov.data2 <- qread("~/Data/Clinical Trial SE/GSE15622_SE.qs")

```


Once again, we have sensitivity/resistance labels. We subset to those patients that received taxol therapy. 

```{r}

myx <- ov.data2$treatment.ch1%in%c("Paclitaxel","Both") 

GJB1.exp <- assay(ov.data2)["ENSG00000169562",myx]

wilcox.test(split(GJB1.exp, ov.data2$response.ch1[myx])[[1]], split(GJB1.exp, ov.data2$response.ch1[myx])[[2]])


boxplot(split(GJB1.exp, ov.data2$response.ch1[myx]))

```

In this dataset, we have both pre and post treatment samples. Lets look at the pre-treatment alone:

```{r}

myx <- ov.data2$treatment.ch1%in%c("Paclitaxel","Both") & grepl("pre", ov.data2$clinical.group.ch1)

GJB1.exp <- assay(ov.data2)["ENSG00000169562",myx]

wilcox.test(split(GJB1.exp, ov.data2$response.ch1[myx])[[1]], split(GJB1.exp, ov.data2$response.ch1[myx])[[2]])

toPlot <- split(GJB1.exp, ov.data2$response.ch1[myx])
names(toPlot) <- c("Resistant","Sensitive")

pdf("figures/GSE15622_gjb1_boxplot.pdf", width = 4, height = 4)
boxplot(toPlot, ylab = "log(RMA Expression)")
dev.off()
boxplot(toPlot, ylab = "log(RMA Expression)")

```

And now the post-treatment:

```{r}

myx <- ov.data2$treatment.ch1%in%c("Paclitaxel","Both") & grepl("post", ov.data2$clinical.group.ch1)

GJB1.exp <- assay(ov.data2)["ENSG00000169562",myx]

wilcox.test(split(GJB1.exp, ov.data2$response.ch1[myx])[[1]], split(GJB1.exp, ov.data2$response.ch1[myx])[[2]])

boxplot(split(GJB1.exp, ov.data2$response.ch1[myx]))

```

It seems in this case, high expression of this marker post-treatment is trending towards predicting poor response. What if we look at the difference between pre/post for the whole cohort:



```{r}

myx <- ov.data2$treatment.ch1%in%c("Paclitaxel","Both")
status <-  ifelse(grepl("post", ov.data2$clinical.group.ch1), "post", "pre")[myx]

GJB1.exp <- assay(ov.data2)["ENSG00000169562",myx]

wilcox.test(split(GJB1.exp, status)[[1]], split(GJB1.exp, status)[[2]])

boxplot(split(GJB1.exp, status))

```
Lets look to see if matched expression changes in a particular way post treatment.

```{r}
myx <- ov.data2$treatment.ch1%in%c("Paclitaxel","Both")

patients_with_two_samples <- names(table(gsub(colData(ov.data2)[myx,c("title")], pat="\\,.*", rep=""))[table(gsub(colData(ov.data2)[myx,c("title")], pat="\\,.*", rep=""))>1])

pre_post_matched <- matrix(NA_real_, nrow=length(patients_with_two_samples), ncol=2)
rownames(pre_post_matched) <- patients_with_two_samples
colnames(pre_post_matched) <- c('Pre-treatment', 'Post-treatment')
for(pt in patients_with_two_samples){
  
  pre_exp <-  assay(ov.data2)["ENSG00000169562",grepl(pat=paste0(pt, ","), ov.data2$title)&grepl("pre",  ov.data2$title)]
  post_exp <-  assay(ov.data2)["ENSG00000169562",grepl(pat=paste0(pt, ","), ov.data2$title)&grepl("post",  ov.data2$title)]
  pre_post_matched[pt,] <- c(pre_exp, post_exp)
}


boxplot(pre_post_matched[,1], pre_post_matched[,2])

wilcox.test(pre_post_matched[,1], pre_post_matched[,2], paired = T)

pre_post_matched <- data.frame(pre_post_matched, check.names = F)


pre_post_matched$response <- sapply(patients_with_two_samples, function(pt) return(unique(ov.data2$response.ch1[grepl(pat=paste0(pt, ","), ov.data2$title)]) ))
pre_post_matched$patient <- rownames(pre_post_matched)
toPlot <- melt(pre_post_matched)


ggplot(toPlot, aes(variable, value)) + geom_violin(fill="grey") + geom_point() + geom_line(aes(group = patient)) + theme_classic() + ylab("") + xlab("GJB1 Expression")

pdf("figures/GSE15622_pre_post_GJB1.pdf", height = 4, width = 4)
ggplot(toPlot, aes(variable, value)) + geom_violin(fill="grey") + geom_point() + geom_line(aes(group = patient)) + theme_classic() + xlab("") + ylab("GJB1 Expression")
dev.off()
```



# GSE31245

```{r}

GSE31245_SE <- qread("~/Data/Clinical Trial SE/GSE31245_SE.qs")

```

```{r}

GJB1.exp <- assay(GSE31245_SE)["ENSG00000169562", ]

surv.data <- colData(GSE31245_SE)[, c("event_occured", "survival_time")]

colnames(surv.data) <- c("event", 'time')
surv.data$time <- as.numeric(surv.data$time)
surv.data$event <- as.numeric(surv.data$event)


surv.data$GJB1 <- ifelse(GJB1.exp <= median(GJB1.exp), "low", "high")


# pdf("figures/GSE31245_surv_gjb1.pdf", height=4, width=4)
p <- ggsurvplot(survfit(Surv(time, event = event) ~ GJB1, surv.data), pval = T)
# dev.off()

ggsave(filename="figures/GSE31245_surv_gjb1.pdf", plot=p$plot, width=4, height = 4)

ggsurvplot(survfit(Surv(time, event = event) ~ GJB1, surv.data), pval = T)


```







