---
title: "Supplementary Figure 9"
output:
  html_document:
    df_print: paged
---

# Sankey/Consort Like Diagrams for Validation Data

## Snakey Diagram Output
```{r}

library(data.table)
library(ggsankey)
library(ggplot2)
library(dplyr)



metaRes <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")




metaRes2 <- metaRes[, `Meta Analysis` := ifelse(FWER_genes < 0.05, "Significant", "Not Significant")]
metaRes2[, `Meta Analysis` := factor(`Meta Analysis`, levels = c("Not Significant", "Significant"))]


metaRes2[`Meta Analysis` %in% "Significant", `Validation Data` := "Not Available"]

metaRes2[`Meta Analysis` %in% "Significant" & ((Drug == "Paclitaxel" & (Tissue %in% c("Breast", "Ovary/Fallopian Tube"))) | (Drug == "Erlotinib" & Tissue == "Lung")), `Validation Data` := "Available"]


metaRes2[`Meta Analysis` %in% "Significant" & ((Drug == "Paclitaxel" & (Tissue %in% c("Breast", "Ovary/Fallopian Tube"))) | (Drug == "Erlotinib" & Tissue == "Lung")), `Clinically Validates` := "No"]

metaRes2[Drug == "Paclitaxel" & Tissue == "Breast" & Gene == "ENSG00000115758", `Clinically Validates` := "Yes"]

metaRes2[Drug == "Erlotinib" & Tissue == "Lung" & Gene == "ENSG00000116670", `Clinically Validates` := "Yes"]
metaRes2 <- metaRes2[, `Dataset Analysis` := "Significant"]

metaRes2 <- metaRes2[, .(`Dataset Analysis`, `Meta Analysis`, `Validation Data`)]



test <- metaRes2 %>% make_long(colnames(metaRes2))

test$node <- factor(test$node, levels = c("Significant", "Not Significant", "Available", "Not Available", "Yes", "No"))
test$next_node <- factor(test$next_node, levels = c("Significant", "Not Significant", "Available", "Not Available", "Yes", "No"))


png("figures/task2Sankey.png", res = 600, width = 6, height = 4, unit = "in")

ggplot(test, aes(
    x = x, next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node, label = node
)) +
    geom_sankey(flow.fill="gray50") +
    geom_sankey_label(size = 3, color = "white", fill = "gray40") +
    scale_fill_viridis_d() +
    theme_sankey(base_size = 18) +
    labs(x = NULL) +
    theme(
        legend.position = "none",
        plot.title = element_text(hjust = .5)
    )
dev.off()


```



## Consort Diagram stats 

Total Number of Triplets investigated
```{r}
library(data.table)
toRunAll <- fread("~/Code/tissue_biomarker/rnaResultsPrism/runlist_files/geneExpressionMasterToRunList.txt", header=F)
metaRes <- fread("~/Code/tissue_biomarker/rnaResultsPrism/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")

toRunAll[,.N]

```


Total Number of Tissue-Drug Pairs Investigated
```{r}
unique(toRunAll[, .(V2, V3)])[,.N]
```

Total number of Pairs Signigicant in 1 dataset 

```{r}
unique(metaRes[, .(Drug, Tissue)])[,.N]

```

Total number of Pairs Signigicant after meta-analysis 

```{r}
unique(metaRes[`FWER_genes` <= 0.05, .(Drug, Tissue)])
```


### Loading in clinical dataset sheet

```{r}

clinicalData <- fread("~/Code/Github/tbp_manuscript_figures/data/All clinical datasets - Non-Immunotherapy datasets.csv")

tissueDrugClin <- clinicalData[,.(`Treatment regimen`, `Standardized Tissue`)]

```

Spliting treatments into components 


```{r}

tdcSplit <- split(tissueDrugClin, by = c("Treatment regimen", "Standardized Tissue"))
tdcSplit <- lapply(tdcSplit, \(dt){
    dt <- unique(dt)
    dt <- dt[,.(unlist(strsplit(`Treatment regimen`, split="\\+|\\||\\,")),`Standardized Tissue`)]
    dt[,V1 := gsub("[A-Z]+\\s\\(|\\(|\\)", x=V1, rep="")]
    return(dt)
})

tissueDrugClinLong <- rbindlist(tdcSplit)
tissueDrugClinLong <- unique(tissueDrugClinLong)
tissueDrugClinLong[,.N]

```

Intersecting with all possible biomarkers 


```{r}

toRunTissueDrug <- unique(toRunAll[, .(V2, V3)])
colnames(tissueDrugClinLong) <- c("Drug", "Tissue")


colnames(toRunTissueDrug) <- c('Tissue', "Drug")

merge(toRunTissueDrug,tissueDrugClinLong, by=c("Drug", "Tissue"))[,.N]

```


Intersecting with dataset specific markers


```{r}
merge(unique(metaRes[,.(Tissue, Drug)]), tissueDrugClinLong, by = c("Drug", "Tissue"))[, .N]

```


Intersecting with meta-analysis markers


```{r}
merge(unique(metaRes[FWER_genes <= 0.05, .(Tissue, Drug)]), tissueDrugClinLong, by = c("Drug", "Tissue"))

```

# Sankey Diagram Attempt #2

The plan here is to make a sankey on the level of drug-tissue/indictations. 

```{r}
library(data.table)
library(ggsankey)
library(ggplot2)
library(dplyr)

toRunTissueDrug[,`Has Clinical Data` := "No"]

toRunTissueDrug[tissueDrugClinLong, `Has Clinical Data` := "Yes", on = .(Drug, Tissue)]
toRunTissueDrug[, table(`Has Clinical Data`)]

toRunTissueDrug[tissueDrugClinLong, `Has Clinical Data` := "Yes", on = .(Drug, Tissue)]

toRunTissueDrug[, `Dataset Specific Marker` := "No"]

toRunTissueDrug[unique(metaRes[,.(Drug, Tissue)]), `Dataset Specific Marker` := "Yes", on = .(Drug, Tissue)]
toRunTissueDrug[, table(`Dataset Specific Marker`)]


toRunTissueDrug[, `Meta-Analysis Marker` := "No"]

toRunTissueDrug[unique(metaRes[FWER_genes <= 0.05, .(Drug, Tissue)]), `Meta-Analysis Marker` := "Yes", on = .(Drug, Tissue)]
toRunTissueDrug[, table(`Meta-Analysis Marker`)]

toRunTissueDrugToPlot <- toRunTissueDrug[, .(`Dataset Specific Marker`, `Meta-Analysis Marker`, `Has Clinical Data`)]


test <- toRunTissueDrugToPlot %>% make_long(colnames(toRunTissueDrugToPlot))

# test$node <- factor(test$node, levels = c("Significant", "Not Significant", "Available", "Not Available", "Yes", "No"))
# test$next_node <- factor(test$next_node, levels = c("Significant", "Not Significant", "Available", "Not Available", "Yes", "No"))

test <- data.table(test)
test[, count := .N, .(x, node)]


ggplot(test, aes(
    x = x, next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node, label = count
)) +
    geom_sankey(flow.fill = "gray60", flow.color="gray30", node.color="gray30", flow.alpha=.70) +
    geom_sankey_label(size = 3, color = "white", fill = "gray30") +
    scale_fill_viridis_d() +
    theme_sankey(base_size = 18) +
    labs(x = NULL, fill = "") +
    theme(
        # legend.position = "none",
    )

pdf("figures/tissue_drug_sankey.pdf", width=10, height=4)
ggplot(test, aes(
    x = x, next_x = next_x,
    node = node,
    next_node = next_node,
    fill = node, label = count
)) +
    geom_sankey(flow.fill = "gray60", flow.color = "gray30", node.color = "gray30", flow.alpha = .70) +
    geom_sankey_label(size = 3, color = "white", fill = "gray30") +
    scale_fill_viridis_d() +
    theme_sankey(base_size = 18) +
    labs(x = NULL, fill = "") +
    theme(
        # legend.position = "none",
    )
dev.off()



# ggplot(test, aes(
#     x = x, next_x = next_x,
#     node = node,
#     next_node = next_node,
#     fill = node, label = node
# )) +
#     geom_alluvial(flow.alpha = .4) +
#     geom_alluvial_label(size = 3, color = "white", fill = "gray40") +
#     scale_fill_viridis_d() +
#     theme_alluvial(base_size = 18) +
#     labs(x = NULL) +
#     theme(
#         legend.position = "none",
#         plot.title = element_text(hjust = .5)
#     )


```

# what about tcga




```{r}
library(readxl)
tcga_drug_annot <- data.table(data.frame(read_excel("~/Code/tissue_biomarker/rnaValidation/clinicalValidation/bioinfo16_supplementary_tables.xlsx", sheet = 3, skip=1)))
tcga_drug_annot[,unique(Cancer)]

tcga.mapping <-fread("~/Code/Github/tbp_manuscript_figures/data/tcga_mapping.csv")

tcga_drug_annot <- merge(tcga_drug_annot, tcga.mapping)



```


Intersecting with all possible biomarkers 


```{r}

toRunTissueDrug <- unique(toRunAll[, .(V2, V3)])
colnames(tissueDrugClinLong) <- c("Drug", "Tissue")

tcga_drug_tissue <- unique(tcga_drug_annot[, c("drug_name", "Standardized Tissue")])
colnames(tcga_drug_tissue) <- c("Drug","Tissue")

merge(tcga_drug_tissue, tissueDrugClinLong, by = c("Drug", "Tissue"))[, .N]

```


Intersecting with dataset specific markers


```{r}
merge(unique(metaRes[, .(Tissue, Drug)]), tcga_drug_tissue, by = c("Drug", "Tissue"))[, .N]

```


Intersecting with meta-analysis markers


```{r}
merge(unique(metaRes[FWER_genes <= 0.05, .(Tissue, Drug)]), tcga_drug_tissue, by = c("Drug", "Tissue"))

```


```{r}
merge(tcga_drug_annot, unique(metaRes[FWER_genes <= 0.05, .(Tissue, Drug)]), by.x = c("drug_name", "Standardized Tissue"), by.y = c("Drug", "Tissue"))[, .N]

```


## compare old vs new


```{r}
oldmetaRes <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/mrna_gene_drug_tissue_res_pharmacodb.csv")

mergedRes <- merge(oldmetaRes,metaRes,all.x=T,all.y=T,by=c("Gene","Drug","Tissue"))

mergedRes[!FWER_genes.x <= 0.05 & FWER_genes.y <= 0.05]

mergedRes[!FWER_genes.x <= 0.05 & FWER_genes.y <= 0.05][,.N,.(Drug,Tissue)]

mergedRes[!FWER_genes.y <= 0.05 & FWER_genes.x <= 0.05][, .N, .(Drug, Tissue)]


```