---
title: "Supplementary Figure 3"
output: html_notebook
---

```{r}
library(PharmacoGx)
library(PRROC)
library(ggplot2)
library(data.table)


biomarker.res <- fread("~/Code/tissue_biomarker/rnaResults/biomarker_res/meta_res_pharmacodb.csv")

toRunByGene <- fread("~/Code/tissue_biomarker/rnaResults/runlist_files/toRunMetaByGene.txt")

colnames(toRunByGene) <- c("Gene", "Tissue", "Drug", "PSet", "Sig")



```



# Comparison to Other Gene Spaces

## First, we will look at whether any of these gene spaces enrich for genes replicating in 

Here, we want to see whether any of the commonly used gene spaces are enriched for genes that validate in meta-analysis. 

### Cancer Gene Census 



```{r}
library(data.table)
library(piano)


cgc.all <- fread("~/Code/tissue_biomarker/cancerGeneCensus/cgc.genes.csv")


cgc.table <- biomarker.res[,table("CGC"=Gene%in%cgc.all$Ensembl.id, "Pass Meta"=BF_p_all<0.05)]

fisher.test(cgc.table)


```


### Hallmarks

```{r}
hallmarks <- loadGSC("~/Code/tissue_biomarker/pathways/h.all.v7.5.1.symbols.gmt")

hallmark.symbols <- unique(unlist(hallmarks$gsc))

gene.info <- fread("~/Code/tissue_biomarker/geneInfo.csv")

hallmark <- na.omit(gsub(pat="\\.[0-9]+$",rep="", gene.info$gene_id[match(hallmark.symbols, gene.info$gene_name)]))

hallmark.table <- biomarker.res[,table("Hallmark"=Gene%in%hallmark, "Pass Meta"=BF_p_all<0.05)]

fisher.test(hallmark.table)

```

### Cancer Functional Events


```{r}
library(readxl)

cfes.all <- read_excel("~/Code/tissue_biomarker/CancerFunctionalEvents/mmc3.xlsx", skip = 2)
cfes.symbol <- unique(cfes.all$Gene)

cfes <- na.omit(gsub(pat="\\.[0-9]+$",rep="", gene.info$gene_id[match(cfes.symbol, gene.info$gene_name)]))


cfes.table <- biomarker.res[,table("CFE"=Gene%in%cfes, "Pass Meta"=BF_p_all<0.05)]

fisher.test(cfes.table)

```

## We also look for overlap enrichment between significant biomarkers at the gene spaces

### Cancer Gene Census

```{r}
library(piano)

sig.gene <- unique(biomarker.res[BF_p_all<0.05, Gene])
gene.info$ensg_clean <- gsub("\\.[0-9]+$", rep="", x=gene.info$gene_id)

universe.of.genes <- unique(toRunByGene$Gene)
universe.of.genes <- intersect(universe.of.genes, gene.info$ensg_clean[gene.info$gene_type%in%"protein_coding"])

allsig.cgc.table <- table("CGC"=unique(toRunByGene$Gene)%in%cgc.all$Ensembl.id, "Signficant"=unique(toRunByGene$Gene)%in%sig.gene )
fisher.test(allsig.cgc.table)
```


### Hallmark

```{r}


allsig.hallmark.table <- table("Hallmark"=universe.of.genes%in%hallmark, "Signficant"=universe.of.genes%in%sig.gene )
fisher.test(allsig.hallmark.table)
allsig.hallmark.table
```



### CFE

```{r}


allsig.cfes.table <- table("CFEs"=universe.of.genes%in%cfes, "Signficant"=universe.of.genes%in%sig.gene )
fisher.test(allsig.cfes.table)
allsig.cfes.table
# fisher.test(allsig.cfes.table)$estimate
```

TODO: Visualization Idea: Heatmap??


## Heatmap



```{r}
library(pheatmap)

pred.sig.vs.all <- c("CGC"=fisher.test(allsig.cgc.table)$estimate[[1]],
                     "Hallmark"=fisher.test(allsig.hallmark.table)$estimate[[1]],
                     "CFEs"=fisher.test(allsig.cfes.table)$estimate[[1]])


pred.meta.pass <- c("CGC"=fisher.test(cgc.table)$estimate[[1]],
                     "Hallmark"=fisher.test(hallmark.table)$estimate[[1]],
                     "CFEs"=fisher.test(cfes.table)$estimate[[1]])

toPlot <- data.matrix(rbind("Significant\nBiomarker"=pred.sig.vs.all, "Pass\nMeta-Analysis"=pred.meta.pass))

pheatmap(toPlot, scale = "none", cluster_rows = F, cluster_cols = F, angle_col = 0)


```

```{r}


getFisherRes <- function(table, name) {
    return(data.frame(
        Geneset = name,
        "Odds Ratio" = fisher.test(table)$estimate[[1]],
        "Lower" = fisher.test(table)$conf.int[1],
        "Upper" = fisher.test(table)$conf.int[2],
        p.val = format(fisher.test(table)$p.val[[1]], scientific=T),
        check.names = FALSE
    ))
}

toPlot <- rbindlist(list(getFisherRes(allsig.cgc.table, "CGC"),
               getFisherRes(allsig.cfes.table, "CFEs"),
               getFisherRes(allsig.hallmark.table, "Hallmark")))


p <- ggplot(toPlot, aes(x = `Odds Ratio`, y = Geneset, xmin = Lower, xmax = Upper, label = p.val)) +
    geom_errorbarh(height = 0.15, show.legend = FALSE) +
    geom_point() +
    geom_vline(xintercept = 1, linetype = 2, show.legend = FALSE) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    geom_text(aes(x = Inf, y = Geneset), nudge_x = 0.0, size = 4, hjust = "outward", show.legend = FALSE) + # scale_y_discrete(breaks=dd$y)  +
    theme(plot.margin = unit(c(1, 8, 1, 1), "lines"), legend.position = "bottom")

print(p)

pdf("figures/significantOddsRatioPlot.pdf", height=5, width=6)
print(p)
dev.off()

```


```{r}


getFisherRes <- function(table, name) {
    return(data.frame(
        Geneset = name,
        "Odds Ratio" = fisher.test(table)$estimate[[1]],
        "Lower" = fisher.test(table)$conf.int[1],
        "Upper" = fisher.test(table)$conf.int[2],
        p.val = format(fisher.test(table)$p.val[[1]], scientific=T),
        check.names = FALSE
    ))
}

toPlot <- rbindlist(list(getFisherRes(cgc.table, "CGC"),
               getFisherRes(cfes.table, "CFEs"),
               getFisherRes(hallmark.table, "Hallmark")))


p <- ggplot(toPlot, aes(x = `Odds Ratio`, y = Geneset, xmin = Lower, xmax = Upper, label = p.val)) +
    geom_errorbarh(height = 0.15, show.legend = FALSE) +
    geom_point() +
    geom_vline(xintercept = 1, linetype = 2, show.legend = FALSE) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    geom_text(aes(x = Inf, y = Geneset), nudge_x = 0.0, size = 4, hjust = "outward", show.legend = FALSE) + # scale_y_discrete(breaks=dd$y)  +
    theme(plot.margin = unit(c(1, 8, 1, 1), "lines"), legend.position = "bottom")

print(p)

pdf("figures/metaPassOddsRatioPlot.pdf", height=5, width=6)
print(p)
dev.off()

```




## Barplots
I think this will look better in barplots
```{r}

pass.meta.genenum <- list(CGC=cgc.table, Hallmark=hallmark.table, "CFE"=cfes.table)

pass.meta.genenum <- lapply(pass.meta.genenum, reshape2::melt)

pass.meta.toPlot <- rbindlist(pass.meta.genenum, idcol = "Database", use.names=FALSE)

colnames(pass.meta.toPlot)[2] <- "In Gene List"
colnames(pass.meta.toPlot)[4] <- "Proportion of Genes"
colnames(pass.meta.toPlot)[3] = "Pass Meta-Analysis"


ggplot(pass.meta.toPlot, aes(x=`In Gene List`, y=`Proportion of Genes`, fill=`Pass Meta-Analysis`)) + geom_col(position = "fill") + facet_grid(~Database) + theme_bw() #+ theme(panel.grid.major.x = element_blank())

```


```{r}

pass.sig.genenum <- list(CGC=allsig.cgc.table, Hallmark=allsig.hallmark.table, "CFE"=allsig.cfes.table)

pass.sig.genenum <- lapply(pass.sig.genenum, reshape2::melt)

pass.sig.toPlot <- rbindlist(pass.sig.genenum, idcol = "Database", use.names=FALSE)

colnames(pass.sig.toPlot)[2] <- "In Gene List"
colnames(pass.sig.toPlot)[4] <- "Proportion of Genes"


ggplot(pass.sig.toPlot, aes(x=`In Gene List`, y=`Proportion of Genes`, fill=`Signficant`)) + geom_col(position = "fill") + facet_grid(~Database)+ theme_bw() + theme(panel.grid.major.x = element_blank())



```

### ORA analysis for Hallmarks

This isn't necessarily important, but for completeness and curiosity we take a look at whether any of the hallmark genesets are enriched in the biomarkers.


```{r}
library(fgsea)
library(ggrepel)


sig.gene.symbol <- na.omit(gene.info$gene_name[match(sig.gene, gene.info$ensg_clean)])
all.gene.symbol <- unique(na.omit(gene.info$gene_name[match(universe.of.genes, gene.info$ensg_clean)]))


hallmark.ora <- fora(pathways = hallmarks$gsc, genes = sig.gene.symbol, universe = all.gene.symbol)

hallmark.ora[,pfer := p.adjust(pval, method="bonf")]

# pdf("hallmark_enrichment_in_significant_genes.pdf", width=10)
ggplot(hallmark.ora, aes(overlap/size*100, -log10(pval))) + geom_point() + xlab("Percent Geneset as Significant Markers") + ylab("-log10(Fisher Test p-Value)") + geom_hline(yintercept = -log10(0.05/nrow(hallmark.ora))) + theme_bw()  + geom_text_repel(data=hallmark.ora[pfer<0.05], aes(label=pathway), show.legend = F)
# dev.off()

```



